### 2017-12-03 Maths Notes/M2/Centres of mass/Centres of mass.tex
Notes Update
Notes update - Centres of mass
M2 Notes update with CoM equilibrium problems

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}

@@

Test

\end{obeylines}

>>>>

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{tabularx}

@@

\end{obeylines}
\newpage
\begin{center}
\underline{\huge Centres of mass example - Equilibrium problems}
\end{center}
\includegraphics[width=1.5in]{Equilibrium_Problem.JPG}\\
\\
\textit{(a) Find the distance of the centre of mass of the lamina from AF. }\\

\textbf{1. Find the masses and locations of all areas or rods and put in a table}\\
\\
{\renewcommand{\arraystretch}{1.5}
\begin{tabularx}{\textwidth}{|X|X|X|}
\hline
Mass(m)&$4a^2$&$-a^2$\\
\hline
Distance From AF(x)&$a$&$\frac{3}{2}a$\\
\hline
mx&$4a^3$&$-\frac{3}{2}a^3$\\
\hline
\end{tabularx}}
\\
\\
\textbf{2. Use the formula to find the centre of mass}\\
\\
\textcolor{red}{$\bar{x}=\dfrac{\Sigma m_ix_i}{\Sigma m_i}$}\\
\\
$\bar{x}=\dfrac{\frac{5}{2}a^3}{3a^2}=\dfrac{5a}{6}$\\
\\
\textit{The lamina is freely suspended from A and hangs in equilibrium.}\\
\textit{(b) Find, in degrees to one decimal place, the angle which AF makes with the vertical.}\\
\\
\textbf{Use symmetry to find the y coordinate of the centre of mass}\\
\\
\begin{tikzpicture}[scale=1.9]
\tikzstyle{ann} = [fill=white,font=\footnotesize,inner sep=1pt]

\draw[black, thick] (0,0) -- (0,2) -- (1,2) -- (1,1) -- (2,1) -- (2,0) -- cycle;
\draw[arrows=<->](0,5/6)--(5/6,5/6);
\node[ann] at (5/12,5/6) {$\frac{5}{6}$};
\draw [blue,dashed] (0,0) -- (2,2);
\draw[arrows=<->](5/6,0)--(5/6,5/6);
\node[ann] at (5/6,5/12) {$\frac{5}{6}$};
\end{tikzpicture}
\\
\\
\textbf{Re-draw to find angle}\\
\begin{tikzpicture}[scale=1.9]
\tikzstyle{ann} = [fill=white,font=\footnotesize,inner sep=1pt]
\tikzstyle{angle} = [fill=none,font=\tiny,inner sep=1pt]
\draw[black, thick] (0,0) -- (0,2) -- (1,2) -- (1,1) -- (2,1) -- (2,0) -- cycle;
\draw[arrows=<->](0,5/6)--(5/6,5/6);
\node[ann] at (5/12,5/6) {$\frac{5}{6}$};
\draw[arrows=<->](5/6,5/6) -- (5/6,2);
\node[ann] at (5/6,17/12) {$\frac{7}{6}$};
\draw [blue,dashed] (0,2) -- (5/6,5/6);
\draw[thick] (5/24,41/24) arc (0:-90:0.2);
\node[ann] at (0.1,1.7) {$\theta$};
\end{tikzpicture}\\
\\
$\tan(\theta)=\dfrac{5/6}{7/6}$\\
\\
$\theta=35.5\degree$
\newpage
